Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
New table 1

@@

@@

<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
 Fri Jun 24 12:02:11 2016 -->
\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{Original\\on Turk?} & N (orig) & N (rep) \\ 
  \hline
Storm \& Stone (2015) & 3 & No & No & No &  48 &  61 \\ 
Lewis \& Oyserman (2015) & 4 & No & Yes & Yes & 122 & 128 \\ 
Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  19 \\ 
Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
Sofer et al. (2015) & 1 & No & Yes & No &  48 &  95 \\ 
Ko, Sadler, \& Galinksy (2015) & 2 & Yes & Some & No &  40 &  40 \\ 
Atir, Rosenzweig, \& Dunning (2015) & 1b & No & Yes & Yes & 202 &  50 \\ 
Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 321 \\ 
Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary of papers and experiments that were targets for replication in our projects.} 
\label{tab:summary}
\end{table}

>>>>

header-includes:
   - \usepackage{lscape}

@@

\begin{landscape}
\centering

@@

\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllr|lrcl}
  \hline
\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Replication\\Support}\\ 
  \hline

Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.50 & Full \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.50 & Full \\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.25 & Partial \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 4.75 & Partial \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.25 & Full \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 4.75 & None \\ 
Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.50 & Partial \\ 
Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & Partial \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.00 & None \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 4.00 & Partial \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.25 & Partial \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary of original research papers and results of experiments that were targets for replication in our projects.} 
\label{tab:summary}
\end{table}

\end{landscape}
